%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\PassOptionsToPackage{colorlinks=true, unicode}{hyperref}
\documentclass[11pt, a4paper, sans]{moderncv}      % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
%
% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{burgundy}                           % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
%
% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
%
% personal data
\name{Scott C.}{Lowe}
%\title{Curriculum Vitae}
% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%
% \address{University of Edinburgh, Informatics Forum, 10 Crichton Street}{Edinburgh, EH8~9AB}{U.K.}
% optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[mobile]{+1~(234)~567~890}
% \phone[fixed]{+44~7010~058~300}% was {+44~7010~039~989}
%\phone[fax]{+3~(456)~789~012}
%
% \email{scottclowe@gmail.com}
\email{scott.lowe@vectorinstitute.ai}
\homepage{scottclowe.com}
\social[linkedin]{scottclowe}
%\social[twitter]{scottclowe}
\social[github]{scottclowe}
\social[kaggle]{scottclowe}
%\social[orcid]{0000-0002-5237-3867}
\social[googlescholar]{ZFPhxuAAAAAJ}
\extrainfo{Nationality: British}
%\photo[64pt][0.4pt]{picture}
% optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}
%
% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}
%
% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------------
%
\usepackage{doi}
\usepackage{multirow}
%
%\usepackage[usenames,dvipsnames]{xcolor}
%\newcommand\href[3][MidnightBlue]{\href{#2}{\color{#1}#3}}
%\newcommand\href[2]{\href{#1}{\textcolor[HTML]{006794}{#2}}}
%
\newcommand\arxiv[1]{arXiv:\href{https://arxiv.org/abs/#1}{#1}}
\newcommand\biorxiv[1]{bioRxiv:\href{https://doi.org/10.1101/#1}{#1}}
%
\newcommand{\AngelChang}[0]{\href{https://angelxuanchang.github.io/}{Angel Chang}}
\newcommand{\LilaKari}[0]{\href{https://cs.uwaterloo.ca/~lila/}{Lila Kari}}
\newcommand{\SageevOore}[0]{\href{https://www.dal.ca/faculty/computerscience/faculty-staff/sageev-oore.html}{Sageev Oore}}
\newcommand{\StefanoPanzeri}[0]{\href{https://www.iit.it/people-details/-/people/stefano-panzeri}{Stefano Panzeri}}
\newcommand{\NathalieRochefort}[0]{\href{https://discovery-brain-sciences.ed.ac.uk/our-staff/research-groups/nathalie-rochefort}{Nathalie Rochefort}}
\newcommand{\MarkvanRossum}[0]{\href{https://www.nottingham.ac.uk/psychology/people/mark.vanrossum}{Mark van Rossum}}
\newcommand{\GrahamTaylor}[0]{\href{https://www.uoguelph.ca/ceps/people/graham-taylor}{Graham Taylor}}
\newcommand{\AlexThiele}[0]{\href{https://www.ncl.ac.uk/psychology/people/profile/alexthiele.html}{Alex Thiele}}
\newcommand{\ThomasTrappenberg}[0]{\href{https://www.dal.ca/faculty/computerscience/faculty-staff/thomas-trappenberg.html}{Thomas Trappenberg}}
%
\begin{document}
%
%------------------------------------------------
\makecvtitle

% Change links to be signified by blue colour
\definecolor{urlcolor}{HTML}{0a2bbf}  % blue  % 0a2bbf or 006794
\definecolor{darkgrey}{rgb}{0.45, 0.45, 0.45}
\hypersetup{linkcolor=darkgrey,citecolor=urlcolor,filecolor=urlcolor,menucolor=urlcolor,runcolor=urlcolor,urlcolor=urlcolor}


\section{Summary}

\cvitem{}{%
Highly accomplished research scientist with a Ph.D. in Neuroinformatics and over a decade of experience in interdisciplinary research bridging cognitive sciences, deep learning, and artificial intelligence. Proven track record in developing advanced ML models, leading innovative projects, supervising students, and publishing impactful research in multidisciplinary collaborations.
}{}{}{}{}{}


\section{Current position}
% Your current or previous employment position

\cventry{since 2022}{Postdoctoral Research Fellow}{Vector Institute}{Toronto, Canada}{}{
\begin{itemize}
  \item Investigating and developing System 2 reasoning capabilities in Large Language Models [\href{https://arxiv.org/abs/2410.03662}{Paper}].
  \item Developing multimodal ML models (vision, DNA, and text) to facilitate monitoring of global insect biodiversity, even on previously unseen species [\href{https://arxiv.org/abs/2406.02465}{Paper}, \href{https://arxiv.org/abs/2405.17537}{Paper}, \href{https://arxiv.org/abs/2311.02401}{Paper}].
  \item Curated and released \href{https://biodiversitygenomics.net/projects/5m-insects/}{BIOSCAN-5M}, a dataset of 5M samples of insects with paired image and DNA barcode data [\href{https://arxiv.org/abs/2406.12723}{Paper}].
  \item Developing real-time, interactive symbolic music generation, using deep state-space models.
\end{itemize}
Responsibilities: lead research projects, supervise students, develop tooling for running experiments used by the rest of the lab.\\
Advisors: Prof. \SageevOore{} and Prof. \GrahamTaylor{}.
}


\section{Education}
% arguments 3 to 6 can be left empty
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\cventry{2012 -- 2017}{Doctor of Philosophy (Ph.D. in Neuroinformatics)}{Institute for Adaptive and Neural Computation, School of Informatics, U. of Edinburgh}{Edinburgh, UK}{}{\href{http://scottclowe.com/LoweSC_PhD_thesis.pdf}{Thesis}: Decoding information from neural populations in the visual cortex.
%\href{http://scottclowe.com/LoweSC_PhD_thesis.pdf}{[Thesis PDF]}.
%\href{http://scottclowe.com/LoweSC_PhD_abstract.pdf}{[Abstract]},
%\href{http://scottclowe.com/LoweSC_PhD_laysummary.pdf}{[Lay Summary]}.
Supervisors: Profs. \MarkvanRossum{}, \StefanoPanzeri{}, and \AlexThiele{}.
}

\cventry{2011 -- 2012}{MSc with Distinction, in Neuroinformatics by Research}{U. of Edinburgh}{Edinburgh, UK}{\textit{average 75.3\%
 --- for comparison, a Distinction at $\ge70\%$ is approximately equivalent to $\ge3.75/4$ US GPA%
}}{%
%\begin{tabular}{lp{11.5cm}}
% & Neural Computation, Principles of Neuroscience, Probabilistic Modelling and Reasoning, Neural Information Processing, Computational Neuroscience of Vision, Neuroinformatics Research, Research Thesis (Neuroinformatics; Topic: \emph{An information theoretic analysis of perceptual learning data from macaque V1 and V4})\\
%\end{tabular}
Thesis: \emph{An information theoretic analysis of perceptual learning data from macaque V1 and V4}.
Supervisors: Prof. \AlexThiele{} and Prof. \StefanoPanzeri{}.
}

\cventry{2007 -- 2011}{MSci with First Class Honours, in Natural Sciences (Mathematics and Physics)}{Durham University}{Durham, UK}{\textit{average 73.4\%
 --- for comparison, a First Class at $\ge70\%$ is approximately equivalent to $\ge3.75/4$ US GPA%
}}{%
%\begin{tabular}{lp{11.5cm}}
%Y1:&~Core Maths A, Core Maths B1, Foundations of Physics 1, Discovery Skills in Physics\\
%Y2:&~Complex Analysis, Linear Algebra, Analysis in Many Variables, Foundations of Physics 2, Thermal and Condensed Matter Physics\\
%Y3:&~Differential Geometry, Dynamical Systems, Continuum Mechanics, Foundations of Physics 3, Theoretical Physics\\
%Y4:&~Elliptic Functions, Mathematical Finance, Partial Differential Equations, Solitons, Project (Mathematics; Topic: \emph{Artifical Neural Networks})\\
%\end{tabular}
Thesis: \emph{On Artifical Neural Networks},  Supervisor: Dr. Ian Jermyn.
}
%
%\cventry{2005--2007}{A-Levels}{Sandbach School}{Cheshire, UK}{}{Mathematics, Further Mathematics, Physics, Chemistry (all grade A).}


%\section{Master thesis}
%\cvitem{title}{\emph{An information theoretic analysis of perceptual learning data from macaque V1 and V4}, Master of Science by Research thesis, University of Edinburgh.}
%\cvitem{year}{2012}
%\cvitem{supervisors}{Alex Thiele and Stefano Panzeri}
%%\cvitem{description}{Short thesis abstract}
%
%
%\section{Master thesis}
%\cvitem{title}{\emph{On Artifical Neural Networks}, Master of Natural Sciences (Mathematics) dissertation, Durham University}
%\cvitem{year}{2011}
%\cvitem{supervisors}{Ian Jermyn}
%%\cvitem{description}{Short thesis abstract}

\clearpage
\section{Experience}

\cventry{2020 -- 2022}{Postdoctoral Research Fellow (Full time)}{Faculty of Computer Science, Dalhousie University}{Halifax, Canada}{}{
\begin{itemize}
  \item Steered research objectives for deployment of deep learning methods on hierarchically-annotated seafloor imagery [\href{https://doi.org/10.1109/CCECE49351.2022.9918377}{Paper}].
  \item Curated and released \href{https://doi.org/10.20383/103.0614}{BenthicNet}, a dataset of 11M seafloor habitat images from 24k sites around the world [\href{https://arxiv.org/abs/2405.05241}{Paper}].
\end{itemize}
Advisor: Prof. \ThomasTrappenberg{}
}

\cventry{2019 -- 2020}{Postdoctoral Research Fellow (Full time)}{Faculty of Computer Science, Dalhousie University}{Halifax}{Canada. Joint affiliation: Dept. of Electrical and Computer Engineering}{
\begin{itemize}
  \item Applied deep learning to CPAP data in partnership with \href{https://novaresp.ai/}{NovaResp}, preemptively predicting sleep apneas, subsequently reducing apneas and hypopneas by 32\% [\href{https://doi.org/10.1109/TBME.2023.3263379}{Paper}, \href{https://doi.org/10.1183/13993003.congress-2023.PA573}{Paper}].
  \item Collaborated with \href{https://fundyforce.ca/}{FORCE}, \href{https://deepsense.ca/}{DeepSense}, and \href{https://oera.ca/}{OERA} to segment echograms of tidal energy sites using deep learning, decreasing errors by 60\% and halving manual labour [\href{https://doi.org/10.3389/fmars.2022.867857}{Paper}].
  \item Initiated research agendas focused on applying ML to healthcare and environmental monitoring, demonstrating leadership in interdisciplinary projects.
\end{itemize}
Advisors: Prof. \SageevOore{}, Prof.~Kamal El-Sankary
}


\cventry{2018 -- 2019}{Postdoctoral Research Fellow (Full time)}{Faculty of Computer Science, Dalhousie University}{Halifax}{Canada. Joint affiliation: Vector Institute}{
\begin{itemize}
  \item Research in novel deep learning methods by deploying logical operations in logit space, inspired by neuroscience [\href{https://papers.nips.cc/paper_files/paper/2022/hash/c05144b635df16ac9bbf8246bbbd55ca-Abstract-Conference.html}{Paper}, \href{https://arxiv.org/abs/2111.01742}{Paper}].
  \item Controllable symbolic music generation [\href{https://arxiv.org/abs/1907.04352}{Paper}].
\end{itemize}
Advisors: Prof. \SageevOore{}, Prof. \ThomasTrappenberg{}.
}

%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.}

% March 2018 to June 2018
\cventry{2018 -- 2018}{Postdoctoral Research Fellow (Full time)}{School of Psychology \& School of Mathematics, University of Nottingham}{Nottingham}{UK}{
	Program synthesis for visual reasoning tasks [\href{https://arxiv.org/abs/1911.07721}{Paper}].
	Advisor: Prof. \MarkvanRossum{}.
}

% March 2017 to August 2017
\cventry{2017 -- 2017}{Co-founder and CSO (Full time)}{Cortirio}{London}{UK}{
  Co-founder and Chief Scientific Officer at \href{https://cortirio.com/}{Cortirio}, developing a portable brain scanner for diagnosing traumatic brain injury.
  Backed by \href{https://www.joinef.com/}{Entrepreneur First}.
}

% March 2017 to August 2017
% \cventry{2017}{Entrepreneurial Fellow (Full time)}{Entrepreneur First}{London}{UK}{
% Exploration of new startup ideas.
% }

% May 2015 to December 2015
\cventry{2015 -- 2015}{Technical Research Assistant (Full time)}{Rochefort Lab, Centre for Integrative Physiology, University of Edinburgh}{Edinburgh}{UK}{
\begin{itemize}
  \item Developed \href{https://github.com/rochefort-lab/fissa}{FISSA}, an open source toolbox for source-separation of neuroscientific calcium imaging data [\href{https://doi.org/10.1038/s41598-018-21640-2}{Paper}].
  \item Developed internal tooling for data analysis, deployed by multiple labs at UoE [\href{https://doi.org/10.7554/eLife.14985}{Paper}].
\end{itemize}
Advisor: Prof. \NathalieRochefort{}.
%\url{https://github.com/rochefort-lab}.
}

% July 2010 to September 2010
% \cventry{2010}{Web Technician (Full time)}{FleXtel Ltd}{Sandbach}{UK}{Programming in PHP for telecoms company. Designed and coded new website selling isolated consumer product. Developed market-leading algorithms to price telephone numbers based on memorability of both numeric patterns and alphadial patterns \href{http://www.flextel.com/numbers/}{http://www.flextel.com/numbers/}.
% }
%
%\cventry{Sep, 2009}{Physics Studentship}{University of Durham}{Durham}{}{Programming in MATLAB to simulate Rydberg atoms and their interactions.}


\section{Additional courses}

\cventry{Oct 2024}{Generative AI with Large Language Models}{deeplearning.ai}{Coursera}{\href{https://coursera.org/share/2432a06648e1e04bb1a9baec4181bb12}{\textit{Grade:~100\%}.}}{}

\cventry{Jul 2018}{Deep Learning \& Reinforcement Learning Summer School 2018}{CIFAR \& Vector Institute}{Toronto, Canada}{\href{https://dlrl.ca/}{DLRLSS2018}.}{}{}

\cventry{Feb 2018}{Deep Learning Specialization}{deeplearning.ai}{Coursera}{\href{https://www.coursera.org/account/accomplishments/specialization/5CPL4FBLZGVA}{\textit{Grade:~100\%}.}}{}

%\cventry{Jan 2018}{Convolutional Neural Networks}{deeplearning.ai}{Coursera}{\href{https://www.coursera.org/account/accomplishments/records/PHGYXP4LKJSN}{\textit{Grade: 100\%}}}{}
%\cventry{Jan 2018}{Improving Deep Neural Networks: Hyperparameter tuning, Regularization and Optimization}{deeplearning.ai}{Coursera}{\href{https://www.coursera.org/account/accomplishments/records/Q5AMGN9Z5J3J}{\textit{Grade: 100\%}}}{}
%\cventry{Jan 2018}{Structuring Machine Learning Projects}{deeplearning.ai}{Coursera}{\href{https://www.coursera.org/account/accomplishments/records/UFZBPEJX4Z2M}{\textit{Grade: 100\%}}}{}
%\cventry{Jan 2018}{Neural Networks and Deep Learning}{deeplearning.ai}{Coursera}{\href{https://www.coursera.org/account/accomplishments/records/29S67P3YK4SR}{\textit{Grade: 100\%}}}{}

\cventry{Aug 2016}{Machine Learning Summer School 2016}{Universidad Cat\'{o}lica}{Arequipa, Peru}{\href{http://mlss.cc/}{MLSS16}.}{}{}

\cventry{Feb 2016}{Machine Learning}{Stanford University}{Coursera}{\href{https://www.coursera.org/account/accomplishments/records/C3BHEHRLC4HT}{\textit{Grade:~100\%}.}}{}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%----------------------------------------------------------------------------------------
\clearpage

\section{Publications}

% % Publications from a BibTeX file without multibib
% %  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
% %  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
% \nocite{*}
% \bibliographystyle{plain}
% \bibliography{publications}    

\subsection{Selected papers}

\cvitem{Oct, 2024}{
  \textbf{Scott C. Lowe},
  ``System 2 reasoning capabilities are nigh''.
  To be presented at the \textit{\href{https://s2r-at-scale-workshop.github.io/}{System 2 Reasoning At Scale} Workshop, Thirty-Eighth Annual Conference on Neural Information Processing Systems (NeurIPS)}.
  \arxiv{2410.03662}.
}

\cvitem{Jun, 2024}{
  Zahra Gharaee*, \textbf{Scott C. Lowe}*, ZeMing Gong*, Pablo Millan Arias*, Nicholas Pellegrino, Austin T. Wang, Joakim Bruslund Haurum, Iuliia Zarubiieva, Lila Kari, Dirk Steinke$^\dagger$, Graham W. Taylor$^\dagger$, Paul Fieguth$^\dagger$, Angel X. Chang$^\dagger$.
  ``BIOSCAN-5M: A Multimodal Dataset for Insect Biodiversity''.
  To appear at the \emph{Thirty-eighth Conference on Neural Information Processing Systems (NeurIPS)}.
  \arxiv{2406.12723}.
}

\cvitem{Jun, 2024}{
  \textbf{Scott C. Lowe}*, Joakim Bruslund Haurum*, Sageev Oore$^\dagger$, Thomas B. Moeslund$^\dagger$, Graham W. Taylor$^\dagger$.
  ``An Empirical Study into Clustering of Unseen Datasets with Self-Supervised Encoders''.
  (Under review.)
  \arxiv{2406.02465}.
}

\cvitem{May, 2024}{
  ZeMing Gong, Austin T. Wang, Joakim Bruslund Haurum, \textbf{Scott C. Lowe}, Graham W. Taylor, Angel X. Chang.
  ``BIOSCAN-CLIP: Bridging Vision and Genomics for Biodiversity Monitoring at Scale''.
  (Under review.)
  \arxiv{2405.17537}.
}

\cvitem{Dec, 2022}{
  \textbf{Scott C. Lowe}, Robert Earle, Jason d'Eon, Thomas Trappenberg, Sageev Oore. (2022, December). ``Logical Activation Functions: Logit-space equivalents of Probabilistic Boolean Operators''.
  In \emph{\href{https://papers.nips.cc/paper_files/paper/2022/hash/c05144b635df16ac9bbf8246bbbd55ca-Abstract-Conference.html}{Proceedings} of the Thirty-sixth Conference on Neural Information Processing Systems}.
  \arxiv{2110.11940}.
}

\cvitem{Aug, 2022}{
  \textbf{Scott C. Lowe}, Louise P. McGarry, Jessica Douglas, Jason Newport, Sageev Oore, Christopher Whidden, Daniel J. Hasselman. (2022, August). ``Echofilter: A Deep Learning Segmentation Model to Improve the Automation, Standardization, and Timeliness for Post-Processing Echosounder Data in Tidal Energy Streams''. \emph{Frontiers in Marine Science}. \textbf{9}:867857.
  \doi{10.3389/fmars.2022.867857}
  \arxiv{2202.09648}.
}


\subsection{Additional papers}

\cvitem{Jun, 2024}{
  D Steinke, S Ratnasingham, J Agda, H Ait Boutou, I Box, M Boyle, D Chan, C Feng, \textbf{SC Lowe}, JTA McKeown, J McLeod, A Sanchez, I Smith, S Walker, CY-Y Wei, PDN Hebert.
  ``Towards a Taxonomy Machine – A Training Set of 5.6 Million Arthropod Images''.
  (Under review.)
  \biorxiv{2024.07.15.600863}.
  \doi{10.1101/2024.07.15.600863}
}

\cvitem{Jun, 2024}{
  I. Xu, B. Misiuk, \textbf{Scott C. Lowe}, M. Gillis, T Trappenberg and C. J. Brown. (June 2024).
  ``Hierarchical Multi-Label Classification with Missing Information for Benthic Habitat Imagery,''
  In Proceedings of the \emph{2024 International Joint Conference on Neural Networks (IJCNN)}.
  doi: \doi{10.1109/IJCNN60899.2024.10650176}.
}

\cvitem{May, 2024}{
  \textbf{Scott C. Lowe}*, Benjamin Misiuk*, Isaac Xu*, Shakhboz Abdulazizov, Amit R. Baroi, Alex C. Bastos, Merlin Best, Vicki Ferrini, Ariell Friedman, Deborah Hart, Ove Hoegh-Guldberg, Daniel Ierodiaconou, Julia Mackin-McLaughlin, Kathryn Markey, Pedro S. Menandro, Jacquomo Monk, Shreya Nemani, John O'Brien, Elizabeth Oh, Luba Y. Reshitnyk, Katleen Robert, Chris M. Roelfsema, Jessica A. Sameoto, Alexandre C. G. Schimel, Jordan A. Thomson, Brittany R. Wilson, Melisa C. Wong, Craig J. Brown$^\dagger$, Thomas Trappenberg$^\dagger$.
  ``BenthicNet: A global compilation of seafloor images for deep learning applications''.
  (Under review.)
  \arxiv{2405.05241}.
}

\cvitem{Dec, 2023}{
  Zahra Gharaee*, ZeMing Gong*, Nicholas Pellegrino*, Iuliia Zarubiieva, Joakim Bruslund Haurum, \textbf{Scott C. Lowe}, Jaclyn T.A. McKeown, Chris C.Y. Ho, Joschka McLeod, Yi-Yun C. Wei, Jireh Agda, Sujeevan Ratnasingham, Dirk Steinke$^\dagger$, Angel X. Chang$^\dagger$, Graham W. Taylor$^\dagger$, Paul Fieguth$^\dagger$. (2023, December).
  ``A Step Towards Worldwide Biodiversity Assessment: The BIOSCAN-1M Insect Dataset''.
  In \emph{\href{https://proceedings.neurips.cc/paper_files/paper/2023/file/87dbbdc3a685a97ad28489a1d57c45c1-Paper-Datasets_and_Benchmarks.pdf}{Proceedings} of the Thirty-seventh Conference on Neural Information Processing Systems (NeurIPS)}.
  \arxiv{2307.10455}.
}

\cvitem{Nov, 2023}{
  Pablo Millan Arias*, Niousha Sadjadi*, Monireh Safari*, ZeMing Gong, Austin T. Wang, \textbf{Scott C. Lowe}, Joakim Bruslund Haurum, Iuliia Zarubiieva, Dirk Steinke, Lila Kari, Angel X. Chang, Graham W. Taylor. (2023, November). ``BarcodeBERT: Transformers for Biodiversity Analysis''.
  (Under review.)
  \arxiv{2311.02401}.
}

\cvitem{Sep, 2023}{
  Hamed Hanafi, Julia Paffile, Meagan Sinclair, Kamal El-Sankary, \textbf{Scott~Lowe}, Sageev Oore, Stephen Driscoll, Thomas Penzel, Ingo Fietze, Sanjay Patel, Reena Mehra, Debra Morrison. (2023, September).
  ``Prevention of obstructive apnea events with machine learning``.
  \emph{European Respiratory Journal}. \textbf{62}(67) PA573.
  \doi{10.1183/13993003.congress-2023.PA573}.
}

\cvitem{Mar, 2023}{
  Meagan Sinclair, Hamed Hanafi Alamdari, Julia Paffile, Kamal El-Sankary, \textbf{Scott~Lowe}, Stephen Driscoll, Sageev Oore, Heather Tomson, Gregory Begin, Guillermo Aristi, Michael Schmidt, David Roach, Thomas Penzel, Ingo Fietze, Sanjay R Patel, Reena Mehra, Debra Morrison. (2023, October).
  ``The Beginning of the AI-Enabled Preventative PAP Therapy Era: A First-in-Human Proof of Concept Interventional Study''.
  \emph{IEEE Transactions on Biomedical Engineering}.
  \doi{10.1109/TBME.2023.3263379}.
}

% \cvitem{Dec, 2022}

\cvitem{Sep, 2022}{
  Isaac Xu, \textbf{Scott C. Lowe}, Thomas Trappenberg. (2022, September).
  ``Label-Free Monitoring of Self-Supervised Learning Progress''.
  \emph{2022 IEEE Canadian Conference on Electrical and Computer Engineering (CCECE)}, Halifax, Nova Scotia, Canada, 2022, pp 78--84.
  \doi{10.1109/CCECE49351.2022.9918377}.
}

% \cvitem{Aug, 2022}

\cvitem{Dec, 2021}{
  Hamed Hanafi Alamdari, Luke Hacquebard, Stephen Driscoll, Kamal El-Sankary, David C Roach, Robin LeBlanc, \textbf{Scott~Lowe}, Sageev Oore, Thomas Penzel, Ingo Fietze, Michael Schmidt, Debra Morrison. (2022, July). ``High Frequency-Low Amplitude Oscillometry: Continuous Unobtrusive Monitoring of Respiratory Function on PAP Machines''.
  In \emph{IEEE Transactions on Biomedical Engineering}, \textbf{69}(7), pp. 2202--2211.
  \doi{10.1109/TBME.2021.3138965}.
}

\cvitem{Nov, 2021}{
  \textbf{Scott C. Lowe}, Thomas Trappenberg, Sageev Oore. (2021, November). ``LogAvgExp Provides a Principled and Performant Global Pooling Operator''.
  \arxiv{2111.01742}.
}

\cvitem{Nov, 2019}{
  Lu Yihe, \textbf{Scott C. Lowe}, Penelope A. Lewis, Mark C. W. van Rossum. (2019, November). ``Program synthesis performance constrained by non-linear spatial relations in Synthetic Visual Reasoning Test''.
  \arxiv{1911.07721}.
}

\cvitem{Jun, 2019}{
  Nicholas Meade*, Nicholas Barreyre*, \textbf{Scott C. Lowe}, Sageev Oore. (2019, June). ``Exploring Conditioning for Generative Music Systems with Human-Interpretable~Controls''. In \emph{\href{http://computationalcreativity.net/iccc2019/assets/iccc_proceedings_2019.pdf}{Proceedings} of the 10\textsuperscript{th} International Conference on Computational Creativity, 2019}.
  \arxiv{1907.04352}.
}

\cvitem{Feb, 2018}{
  Sander W. Keemink*, \textbf{Scott C. Lowe*}, Janelle M. P. Pakan, Mark C. W. van Rossum, Nathalie L. Rochefort. (2018, February). ``FISSA: A neuropil decontamination toolbox for calcium imaging signals''. \emph{Scientific Reports}, \textbf{8}.
  \doi{10.1038/s41598-018-21640-2}.
}

\cvitem{Jan, 2018}{
  Daniel Zaldivar, Jozien Goense, \textbf{Scott C. Lowe}, Nikos K. Logothetis, Stefano Panzeri. (2018, January). ``Dopamine is signaled by mid-frequency oscillations and boosts output-layers visual information in visual cortex''. \emph{Current Biology}, \textbf{28}(2).
  \doi{10.1016/j.cub.2017.12.006}.
}

\cvitem{Aug, 2016}{
  Janelle M. P. Pakan, \textbf{Scott C. Lowe}, Evelyn Dylda, Sander W. Keemink, Stephen P. Currie, Christopher A. Coutts, Nathalie L. I. Rochefort. (2016, August). ``Behavioral-state modulation of inhibition is context-dependent and cell type specific in mouse visual cortex''. \emph{eLIFE}, \textbf{5}:e14985.
  \doi{10.7554/eLife.14985}.
}

\cvitem{Sep, 2015}{
  Michel Besserve, \textbf{Scott C. Lowe}, Nikos, K. Logothetis, Bernhard Sch\"{o}lkopf, Stefano Panzeri. (2015, September). ``Shifts of gamma phase across primary visual cortical sites reflect dynamic stimulus modulated information transfer''. \emph{PLoS Biology}, \textbf{13}(9): e1002257.
  \doi{10.1371/journal.pbio.1002257}.
}

%\cvitem{\textit{in preparation}}{
%\textbf{Scott C. Lowe}, Daniel Zaldivar, Yusuke Murayama, Mark C. W. van Rossum, Nikos K. Logothetis, Stefano Panzeri (to be submitted). ``Lamina and Frequency Distribution of Information in Primary Visual Cortex''.
%}

%\cvitem{\textit{in preparation}}{
%\textbf{Scott C. Lowe}, Xing Chen, Alex Thiele, Mark C. W. van Rossum, Stefano Panzeri (in preparation). ``Changes in V1 and V4 encoding of visual contrast during perceptual learning''.
%}

% \cvitem{---}{
% \textbf{Scott C. Lowe}, Finlay Maguire, Gavin Gray (in preparation). ``Predicting the onset of epileptic seizures from intracranial-EEG: which features are most useful''.
% }

% \clearpage
\subsection{Talks}

\cvitem{Apr, 2024}{
  \textbf{Scott C. Lowe}. (2024, April).
  ``Self-Supervised Learning Methodology''.
  Presented at the \textit{Self-Supervised Learning Bootcamp}, Vector Institute, Toronto, Canada, 2024.
}

\cvitem{Sep, 2023}{
  \textbf{Scott C. Lowe}. (2023, September).
  ``Single-modal self-supervised learning methods \& background''.
  Presented at the \textit{Self-Supervised Learning Bootcamp}, Vector Institute, Toronto, Canada, 2023.
}

\cvitem{Feb, 2023}{
  \textbf{Scott C. Lowe}. (2023, February).
  ``Tutorial: Self-supervised learning methods''.
  Presented at the \textit{Self-Supervised Learning Reading Group}, Vector Institute, Toronto, Canada, 2023.
}

\cvitem{Jul, 2022}{
  \textbf{Scott C. Lowe}, Robert Earle, Jason d'Eon, Thomas Trappenberg, Sageev Oore. (2022, July).
  ``Logical Activation Functions'' (Spotlight talk).
  Presented at the \textit{\href{https://beyond-bayes.github.io/}{Beyond Bayes: Paths Towards Universal Reasoning Systems Workshop}, 39th International Conference on Machine Learning (ICML)}, Baltimore, Maryland, USA, 2022.
}

\cvitem{May, 2022}{
  Craig J. Brown, Ben Misiuk, Ben DiTrolio, Thomas Trappenburg, \textbf{Scott C. Lowe}, Katleen Robert. (2022, May).
  ``Benthic Ecosystem Mapping For Sustainable Ocean Stewardship In A Shifting Ocean Climate''.
	Presented at \emph{\href{https://geohab.org/wp-content/uploads/2022/05/Abstract_Volume_GEOHAB2022.pdf}{Geohab 2022}}, Venice, Italy.
}

\cvitem{May, 2022}{
  Ben Misiuk, Craig J. Brown, Vicki Ferrini, \textbf{Scott C. Lowe}, Thomas Trappenburg. (2022, May).
  ``Comparing Manual And Automated Feature Engineering Approaches For Mapping Seabed Sediments In The Bay Of Fundy, Canada''.
	Presented at \emph{\href{https://geohab.org/wp-content/uploads/2022/05/Abstract_Volume_GEOHAB2022.pdf}{Geohab 2022}}, Venice, Italy.
}

\cvitem{Feb, 2022}{
  Louise P. McGarry, \textbf{Scott C. Lowe}, Jessica Douglas, Jason Newport, Sageev Oore, Christopher Whidden, and Daniel J. Hasselman. (2022, Mar).
	``Echofilter: A Deep Learning Segmentation Model Improves The Automation, Standardization, And Timeliness For Post-Processing And Reporting Echosounder Data In Tidal Energy Streams''.
	Presented at \emph{Ocean Sciences 2022 (\href{https://www.aslo.org/osm2022/}{OSM 2022})}, Virtual.
}

\cvitem{Jul, 2021}{
	Isaac Xu, Thomas Trappenberg, \textbf{Scott C. Lowe}. (2021, July).
	``Toward Semi-Supervised Classification of Underwater Benthic Habitat Imagery''.
	Presented at \emph{Dalhousie Computer Science In-House Conference (\href{https://dcsi.cs.dal.ca/?page_id=85}{DCSI})}, Dalhousie University, Halifax, Canada.
}

\cvitem{Jul, 2021}{
	Shakhboz Abdulazizov, Thomas Trappenberg, \textbf{Scott C. Lowe}. (2021, July).
	``An Autoencoder Model of Bathymetry and Multibeam Echosound Backscatter''.
	Presented at \emph{Dalhousie Computer Science In-House Conference (\href{https://dcsi.cs.dal.ca/?page_id=85}{DCSI})}, Dalhousie University, Halifax, Canada.
}

\cvitem{Jun, 2021}{
Chris Whidden, Jason Newport, \textbf{Scott C. Lowe}. (2021, June).
``Automating the post-processing of noisy hydroacoustic fish surveying for monitoring tidal turbines''.
{Presented at \emph{International Conference on Ocean Energy}, Madrid, Spain (Virtual).}
}

\cvitem{Oct, 2019}{
Nicholas Barreyre*, Nicholas Meade*, Sageev Oore, Vlado Keselj, \textbf{Scott C. Lowe}. (2019, October).
``Bitwise Conditional Controls Over Language Models for Music and Text''.
{Presented at the \emph{2019 Science Atlantic Conference for Mathematics, Statistics and Computer Science}, Dalhousie University, Halifax, Canada.}
{\textbf{Awarded third place}.}
}

\cvitem{May, 2015}{
\textbf{Scott C. Lowe}, Daniel Zaldivar, Yusuke Murayama, Mark C. W. van Rossum, Nikos K. Logothetis, Stefano Panzeri. (2015, May). ``What does LFP encode?''.
{Presented at the \emph{CINPLA Workshop: ``Inferring network activity from LFPs''}, University of Oslo, Oslo, Norway.}
}

\cvitem{Jan, 2014}{
 \textbf{Scott C. Lowe}, Daniel Zaldivar, Yusuke Murayama, Mark C. W. van Rossum, Nikos K. Logothetis, Stefano Panzeri. (2014, January).``Independent channels of information in visual cortical Local Field
 Potentials''.
 {Presented at the \emph{Institute for Adaptive and Neural Computation Workshop, Jan 14, 2014}, Edinburgh.}
}


\subsection{Workshop/Poster Presentations}

% \textbf{Scott C. Lowe}*, Joakim Bruslund Haurum*, Sageev Oore$^\dagger$, Thomas B. Moeslund$^\dagger$, Graham W. Taylor$^\dagger$,
\cvitem{Jul, 2024}{
  \textbf{SC Lowe}*, J Bruslund Haurum*, S Oore$^\dagger$, TB Moeslund$^\dagger$, GW Taylor$^\dagger$.
  (2024, July).
  ``An Empirical Study into Clustering of Unseen Datasets with Self-Supervised Foundation Models''.
  Presented at the \textit{\href{https://icml-fm-wild.github.io/}{Foundation Models in the Wild} Workshop, The Forty-first International Conference on Machine Learning (ICML)}, Wien (Vienna), Austria, 2024.
  [\href{https://openreview.net/forum?id=kcgf3istoO}{OpenReview}]
}

% ZeMing Gong, Austin T. Wang, Joakim Bruslund Haurum, \textbf{Scott C. Lowe}, Graham W. Taylor, Angel X. Chang
\cvitem{Jun, 2024}{
  Z Gong, AT Wang, J Bruslund Haurum, \textbf{SC Lowe}, GW Taylor, AX Chang.
  (2024, June).
  ``BIOSCAN-CLIP: Bridging Vision and Genomics for Biodiversity Monitoring at Scale``.
  Presented at the \textit{\href{https://sites.google.com/view/fgvc11}{The Eleventh Workshop on Fine-Grained Visual Categorization (FGVC11)}, The IEEE / CVF Computer Vision and Pattern Recognition Conference (CVPR)}, Seattle, USA, 2024.
  [\href{https://drive.google.com/file/d/1S4B9eaUmPPJec7pENFov3_RjryQh-GdX/view?usp=drive_link}{PDF}]
}

% ZeMing Gong, Austin T. Wang, Joakim Bruslund Haurum, \textbf{Scott C. Lowe}, Graham W. Taylor, Angel X. Chang
\cvitem{May, 2024}{
  Z Gong, AT Wang, J Bruslund Haurum, \textbf{SC Lowe}, GW Taylor, AX Chang.
  (2024, May).
  ``BIOSCAN-CLIP: Bridging Vision and Genomics for Biodiversity Monitoring at Scale``.
  Presented at the \textit{\href{https://www.computerrobotvision.org/}{21st Conference on Robots and Vision (CRV)}}, Guelph, Ontario, 2024.
  [\href{https://openreview.net/forum?id=cNPo8e3DmQ}{OpenReview}].
  \textbf{Selected for oral presentation}.
}

% \textbf{Scott C. Lowe}*, Joakim Bruslund Haurum*, Sageev Oore$^\dagger$, Thomas B. Moeslund$^\dagger$, Graham W. Taylor$^\dagger$,
\cvitem{Mar, 2024}{
  \textbf{SC Lowe}*, J Bruslund Haurum*, S Oore$^\dagger$, TB Moeslund$^\dagger$, GW Taylor$^\dagger$.
  (2024, March).
  ``Zero-shot Clustering of Embeddings with Pretrained and Self-Supervised Learnt Encoders''.
  Presented at the \textit{\href{https://vectorinstitute.ai/vector-institute-computer-vision-workshop-showcases-the-fields-current-capabilities-and-future-potential/}{Vector Institute Computer Vision Workshop}}, Toronto, Canada, 2024.
}

% \textbf{Scott C. Lowe}*, Joakim Bruslund Haurum*, Sageev Oore$^\dagger$, Thomas B. Moeslund$^\dagger$, Graham W. Taylor$^\dagger$,
\cvitem{Dec, 2023}{
  \textbf{SC Lowe}*, J Bruslund Haurum*, S Oore$^\dagger$, TB Moeslund$^\dagger$, GW Taylor$^\dagger$.
  (2023, December).
  ``Zero-shot Clustering of Embeddings with Pretrained and Self-Supervised Learnt Encoders''.
  Presented at the \textit{\href{https://sites.google.com/view/r0-fomo}{R0-FoMo: Robustness of Few-shot and Zero-shot Learning in Foundation Models}, 37th Conference on Neural Information Processing Systems (NeurIPS)}, New Orleans, Louisiana, USA, 2023.
  [\href{https://openreview.net/forum?id=2gytoWpJGf}{OpenReview}]
}

% Pablo Millan Arias*, Niousha Sadjadi*, Monireh Safari*, ZeMing Gong, Austin Wang, \textbf{Scott Lowe}, Joakim Haurum, Iuliia Zarubiieva, Dirk Steinke, Lila Kari, Angel Chang, Graham Taylor.
\cvitem{Dec, 2023}{
  P Millan Arias*, N Sadjadi*, M Safari*, Z Gong, A. Wang, \textbf{S Lowe}, J Haurum, I Zarubiieva, D Steinke, L Kari, A Chang, G Taylor.
  (2023, December).
  ``BarcodeBERT: Transformers for Biodiversity Analysis''.
  Presented at the \textit{\href{https://sslneurips23.github.io/}{Self-Supervised Learning --- Theory and Practice}, 37th Conference on Neural Information Processing Systems (NeurIPS)}, New Orleans, Louisiana, USA, 2023.
  [\href{https://sslneurips23.github.io/paper_pdfs/paper_37.pdf}{PDF}]
}

% \textbf{Scott C. Lowe}*, Joakim Bruslund Haurum*, Sageev Oore$^\dagger$, Thomas B. Moeslund$^\dagger$, Graham W. Taylor$^\dagger$,
\cvitem{Dec, 2023}{
  \textbf{SC Lowe}*, J Bruslund Haurum*, S Oore$^\dagger$, TB Moeslund$^\dagger$, GW Taylor$^\dagger$.
  (2023, December).
  ``Zero-shot Clustering of Embeddings with Self-Supervised Learnt Encoders''.
  Presented at the \textit{\href{https://sslneurips23.github.io/}{Self-Supervised Learning --- Theory and Practice}, 37th Conference on Neural Information Processing Systems (NeurIPS)}, New Orleans, Louisiana, USA, 2023.
  [\href{https://sslneurips23.github.io/paper_pdfs/paper_70.pdf}{PDF}]
}

% Isaac Xu, \textbf{Scott C. Lowe}, Thomas Trappenberg. (2022, September).
\cvitem{Sep, 2022}{
I Xu, \textbf{SC Lowe}, T Trappenberg. (2022, September).
``Label-Free Monitoring of Self-Supervised Learning Progress''.
Presented at the \textit{2022 IEEE Canadian Conference on Electrical and Computer Engineering (CCECE)}, Halifax, Nova Scotia, Canada, 2022.
}

% \textbf{Scott C. Lowe}, Robert Earle, Jason d'Eon, Thomas Trappenberg, Sageev Oore. (2022, July).
\cvitem{Jul, 2022}{
\textbf{SC Lowe}, R Earle, J d'Eon, T Trappenberg, S Oore. (2022, July).
``Logical Activation Functions: Logit-space equivalents of Probabilistic Boolean Operators''.
Presented at the \textit{\href{https://beyond-bayes.github.io/}{Beyond Bayes: Paths Towards Universal Reasoning Systems Workshop}, 39th International Conference on Machine Learning (ICML)}, Baltimore, Maryland, USA, 2022.
{\textbf{Selected for spotlight talk}.}
}

% \textbf{Scott C. Lowe}, Robert Earle, Thomas Trappenberg, Sageev Oore. (2020, November).
\cvitem{Nov, 2020}{
\textbf{SC Lowe}, R Earle, T Trappenberg, S Oore. (2020, November).
``Higher Order Activation Functions''.
Presented at \emph{From Neuroscience to Artificially Intelligent Systems (\href{https://meetings.cshl.edu/abstracts.aspx?meet=naisys&year=20}{NAISys})}, Cold Spring Harbor Laboratory, NY, USA.
}

% \textbf{Scott C. Lowe}, Thomas Trappenberg, Sageev Oore. (2019, October).
\cvitem{Oct, 2019}{
\textbf{SC Lowe}, T Trappenberg, S Oore. (2019, October).
``LogAvgExp Provides a Principled and Performant Global Pooling Operator''.
Presented at the \emph{Evolution of Deep Learning Symposium}, Toronto, Canada.
}

% Sofia I. R. Pereira, Natalie Gunasekara, \textbf{Scott C. Lowe}, Mark van Rossum, Penelope A. Lewis. (2019, March). ``Sleep and creativity: differential effects on abstraction
\cvitem{Mar, 2019}{
SIR Pereira, N Gunasekara, \textbf{SC Lowe}, MCW van Rossum, PA Lewis. (2019, March).
``Sleep and creativity: differential effects on abstraction and analogical reasoning''.
Presented at the \emph{26th Annual Meeting of the Cognitive Neuroscience Society}, San Francisco, USA.
}

% Sofia I. R. Pereira, Natalie Gunasekara, \textbf{Scott C. Lowe}, Mark van Rossum, Penelope A. Lewis. (2019, March). ``Sleep and creativity: differential effects on abstraction
\cvitem{Mar, 2019}{
SIR Pereira, N Gunasekara, \textbf{SC Lowe}, MCW van Rossum, PA Lewis. (2019, March).
``Sleep and creativity: differential effects on abstraction and analogical reasoning''.
Presented at the \emph{5th Meeting of the Society for the Neuroscience of Creativity}, San Francisco, USA.
\textbf{Awarded first place}.
}

\cvitem{Nov, 2016}{
D Zaldivar, J Goense, \textbf{SC Lowe}, NK Logothetis, S Panzeri. (2016, November). ``Dopamine elicits lamina-and frequency-specific increase of information in the local-field-potentials of the macaque V1''.
Presented at the \emph{2016 Meeting of the Society for Neuroscience}, San Diego, USA. Program No. \href{http://www.abstractsonline.com/pp8/index.html\#!/4071/presentation/6809}{712.08}.
}

% Pakan, J.M.P, Lowe S.C., Dylda E., Keemink S.W., Currie, S.P., Coutts C.A. and Rochefort N.L.
\cvitem{Jul, 2016}{
JMP Pakan, \textbf{SC Lowe}, E Dylda, SW Keemink, SP Currie, CA Coutts, NL Rochefort. (2016, July). ``Behavioural state modulation of inhibitory activity is context-dependent and cell-type specific in mouse V1.''
Presented at the \emph{10th FENS Forum of Neuroscience}, Copenhagen, Denmark.
}

% Pakan, J.M.P, Lowe S.C., Dylda E., Keemink S.W., Coutts C.A. and Rochefort N.L.
\cvitem{Apr, 2016}{
JMP Pakan, \textbf{SC Lowe}, E Dylda, SW Keemink, CA Coutts, NL Rochefort. (2016, April). ``Sensory context and state-dependent modulation of inhibitory circuit activity in mouse V1''.
Presented at the \emph{The Brain in Focus: New Approaches to Imaging Neurons and Neural Circuits}, Copenhagen, Denmark.
}

% Sander W. Keemink, Janelle M.P. Pakan, \textbf{Scott C. Lowe}, Evelyn Dylda, Mark C.W. van Rossum, Nathalie L. Rochefort. EVCM
\cvitem{Sep, 2016}{
SW Keemink, JMP Pakan, \textbf{SC Lowe}, E Dylda, MCW van Rossum, NL Rochefort. (2016, September). ``Independent Component Analysis (ICA) approach to extract GCampP6-somatic signals from neuropil contamination''.
Presented at the \emph{5th European Visual Cortex Meeting}, Kloster Seeon, Munich, Germany.
}

% Pakan, J.M.P, Lowe S.C., Dylda E., Keemink S.W., Coutts C.A. and Rochefort N.L.
\cvitem{Sep, 2016}{
JMP Pakan, \textbf{SC Lowe}, E Dylda, SW Keemink, CA Coutts, NL Rochefort. (2016, September). ``Context-dependent activity of inhibitory circuits in V1 during locomotion''.
Presented at the \emph{5th European Visual Cortex Meeting}, Kloster Seeon, Munich, Germany.
}

\cvitem{Apr, 2015}{
\textbf{SC Lowe}, D Zaldivar, Y Murayama, MCW van Rossum, NK Logothetis, S Panzeri. (2015, April). ``Cortical dynamics across V1 laminae generate independent frequency channels encoding visual information''.
Presented at the \emph{BNA2015: Festival of Neuroscience}, Edinburgh, UK. Poster Reference: \href{https://www.bna.org.uk/media/resources/files/BNA2015-Abstract-Book.pdf}{P2-C-029}.
%\href{http://www.bna.org.uk/static/docs/BNA2015/BNA2015-Abstract-Book.pdf}{old url}
}

\cvitem{Nov, 2014}{
\textbf{SC Lowe}, D Zaldivar, Y Murayama, MCW van Rossum, NK Logothetis, S Panzeri. (2014, November). ``Different cortical layers in V1 encode different visual information in different frequency bands''.
Presented at the \emph{2014 Meeting of the Society for Neuroscience}, Washington DC, USA. Program No. \href{http://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=a018159d-9116-492d-b234-b4c53acd5260&cKey=e909b23c-40c3-4371-8816-345dfe3e6c3c&mKey=54c85d94-6d69-4b09-afaa-502c0e680ca7}{532.19}.
}

\cvitem{Jul, 2014}{
\textbf{SC Lowe}, D Zaldivar, Y Murayama, MCW van Rossum, NK Logothetis, S Panzeri. (2014, July). ``Quantification of the Laminar and Frequency Structure of Information in Primary Visual Cortex''.
Presented at the \emph{9th FENS Forum of Neuroscience}, Milan, Italy. Abstract number {FENS-2860}.%\href{http://fens2014.meetingxpert.net/FENS_427/poster_102139/program.aspx}{old url}
}

\cvitem{Jul, 2014}{
\textbf{SC Lowe}, D Zaldivar, Y Murayama, MCW van Rossum, NK Logothetis, S Panzeri. (2014, July). ``Quantification of the Laminar and Frequency Structure of Information in Primary Visual Cortex''.
Presented at the \emph{AREADNE 2014 session}, Santorini, Greece.
}

\cvitem{Nov, 2013}{
\textbf{SC Lowe}, X Chen, MCW van Rossum, S Panzeri, A Thiele. (2013, November). ``Decoding spiking activity in V4, but not V1, correlates with behaviour in perceptual learning''.
Presented at the \emph{2013 Meeting of the Society for Neuroscience}, San Diego, USA. Program No. \href{http://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=a69ca081-1031-4c5e-917c-b57b7b7255cf&cKey=5e73e1d9-7177-4207-9890-3efb2a57985b&mKey=8d2a5bec-4825-4cd6-9439-b42bb151d1cf}{555.11.}
}

\cvitem{Jul, 2013}{
  \textbf{SC Lowe}, X Chen, MCW van Rossum, S Panzeri, A Thiele. (2013, July). ``Decoding spiking activity in V4, but not V1, correlates with behavioural performance in perceptual learning task''.
  Presented at the \emph{Twenty Second Annual Computational Neuroscience Meeting: CNS*2013}, Paris, France.
  \emph{BMC Neuroscience} 2013, \textbf{14}(Suppl 1):P385
  \doi{10.1186/1471-2202-14-S1-P385}.
}


%----------------------------------------------------------------------------------------
\clearpage

\section{Technical Skills}

\cvitem{Programming}{Python, MATLAB, Bash/shell, regex, C/C++}
\cvitem{ML}{PyTorch, TensorFlow, PyTorch-Lightning, Scikit-learn, fastAI, Theano, Lasagne}
\cvitem{Development}{Git, pre-commit, TDD, CI/CD, GHA}
\cvitem{Job Scheduler}{Slurm, LSF}
\cvitem{Cloud comp.}{AWS, GCP}
\cvitem{Web}{PHP, JavaScript, AJAX, HTML5, CSS3}
\cvitem{Markup}{Markdown, rST, YAML, JSON, TOML, XML}
\cvitem{Database}{SQL, MySQL}


%----------------------------------------------------------------------------------------
%	GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Grants, honors \& awards}

\cvitem{2022}{
Awarded Mitacs Accelerate grant IT27877: Artificial intelligence driven monitoring and prediction of true sleep health on CPAP machines to improve patient care and reduce the harm of obstructive sleep apnea. \textit{Total value: CAD\,180,000.}
}

\cvitem{2021}{
Compute Canada Resources for Research Groups (RRG) competition, 2021. Project: ``Global Benthic Habitats''. \textit{Value: CAD\,20,059.}
}

\cvitem{2020}{
Awarded Mitacs Accelerate grant IT19053: Monitoring and Analysis of COVID-19 Acute Respiratory Distress Syndrome on Ventilators. \textit{Total value: CAD\,210,000}.
}

\cvitem{2019}{
Awarded Mitacs Accelerate grant IT16140: Active Learning for Fish School Recognition in Echograms in the Bay of Fundy. \textit{Value: CAD\,15,000.}
}

\cvitem{2018}{
Awarded an NVIDIA GPU Grant (Titan~V).
}

\cvitem{2017}{
Placed 8th out of 91 in \href{https://www.kaggle.com/c/nips-2017-non-targeted-adversarial-attack}{NIPS 2017: Non-targeted Adversarial Attack} competition, NIPS2017 Conference Competition Track, organised by Google Brain and Kaggle.
}

\cvitem{2016}{
Awarded a entrepreneurial fellowship with \href{https://joinef.com}{Entrepreneur First}, London.
}

\cvitem{2015}{
Placed 57th out of 1049 in the \href{https://www.kaggle.com/c/datasciencebowl}{National Data Science Bowl} plankton species classification challenge, hosted by Kaggle.
}

\cvitem{2014}{
Placed 16th out of 504 in the \href{https://www.kaggle.com/c/seizure-prediction}{American Epilepsy Society Seizure Prediction Challenge}, hosted by Kaggle.
}

\cvitem{2013}{
Winner of ``Most Viable Business Idea'' award, \href{http://www.meetup.com/Amazon-UK-Hackathon-Group/events/108265382/}{Amazon Scotland Hackathon 2013}.
}

\cvitem{2011}{
Awarded a 4-year scholarship by the University of Edinburgh School of Informatics Doctoral Training Centre in Neuroinformatics, with funding from grants EP/F500385/1 and  BB/F529254/1 from the UK Engineering and Physical Sciences Research Council (EPSRC), UK Biotechnology and Biological Sciences Research Council (BBSRC), and the UK Medical Research Council (MRC).
}

%\cvitem{2007}{
%Awarded the Sandbach School \textit{Boarders Trophy for Excellence in Mathematics}.
%}


% \clearpage
%------------------------------------------------
\section{Open source projects}

\cventry{2024}{bioscan-dataset}{PyTorch torchvision-style datasets for BIOSCAN-1M and BIOSCAN-5M}{available on \href{https://github.com/bioscan-ml/dataset}{GitHub}.}{}{}%  and \href{https://pypi.python.org/pypi/bioscan-dataset}{PyPI}

\cventry{2024}{wandb\_preempt}{Checkpointer for handling preempted Weights \& Biases sweeps on Slurm}{available on \href{https://github.com/f-dangel/wandb_preempt}{GitHub} and \href{https://pypi.python.org/pypi/wandb_preempt}{PyPI}.}{}{}

\cventry{2024}{PyTorch Experiment Template}{A template repository to use for pytorch projects and experiments}{available on \href{https://https://github.com/scottclowe/pytorch-experiment-template}{GitHub}.}{}{}

\cventry{2022}{Echofilter}{Automatically segment echograms (pictures of the water column acquired with echosound) to identify entrained air, sea surface, and seafloor boundaries}{available on \href{https://github.com/DeepSenseCA/echofilter}{GitHub}.}{}{}

\cventry{2020}{Python Template Repo}{A template repository to use for python projects and packages}{available on \href{https://github.com/scottclowe/python-template-repo}{GitHub}.}{}{}

\cventry{2018}{FISSA}{A Python library for decontaminating somatic signals from 2-photon calcium imaging data}{available on \href{https://github.com/rochefort-lab/fissa}{GitHub} and \href{https://pypi.python.org/pypi/fissa}{PyPI}.}{}{}

\cventry{2016}{Superbar}{Multi-colour bar charts for MATLAB, including customisable error bars and significance comparisons}{available on \href{https://github.com/scottclowe/superbar/}{GitHub}, and \href{http://mathworks.com/matlabcentral/fileexchange/57499-superbar}{MATLAB FileExchange}.}{}{}

\cventry{2016}{MOPI: MATLAB/Octave Package Installer}{A simple and flexible package manager for both MATLAB and Octave}{available on \href{https://github.com/mopify/mopi}{GitHub}.}{}{}

\cventry{2015}{MATLAB Schemer}{A colour scheme manager for MATLAB}{available on \href{https://github.com/scottclowe/matlab-schemer}{GitHub}, and through \href{http://mathworks.com/matlabcentral/fileexchange/53862-matlab-schemer}{MATLAB FileExchange}.}{}{}

\cventry{2013}{Colorlab}{Perceptually uniform colormap generation}{available on \href{https://github.com/scottclowe/colorlab}{GitHub}.}{}{}


%----------------------------------------------------------------------------------------
\section{Conference and Seminar Participation}

\cvitem{since 2022}{Vector Institute's \emph{Self-Supervised Learning and Foundation Models} Reading Group Organizer.}{}{}{}{}{}
\cvitem{2024}{Reviewer for \emph{The Thirteenth International Conference on Learning Representations (ICLR).}}{}{}{}{}{}
\cvitem{2024}{Reviewer for \emph{Thirty-eighth Conference on Neural Information Processing Systems (NeurIPS).}}{}{}{}{}{}
\cvitem{2023}{Reviewer for \emph{Thirty-seventh Conference on Neural Information Processing Systems (NeurIPS).}}{}{}{}{}{}
\cvitem{2021}{Reviewer for eLife.}{}{}{}{}{}


%----------------------------------------------------------------------------------------
\section{Patents}

\cvitem{2023}{
Hamed Hanafialamdari, \textbf{Scott~Lowe}, Stephen Driscoll, Luke Hacquebard, David Cecil Roach, Klaus Michael Schmidt. (Novaresp Technologies Inc),
``Method and apparatus for determining and/or predicting sleep and respiratory behaviours for management of airway pressure''.
\href{https://patents.google.com/patent/US11612708B2/en}{US11612708B2}.
}

%----------------------------------------------------------------------------------------
% \clearpage

\section{Media coverage}

\cvitem{Nov, 2021}{
	``Dr. Scott C. Lowe'', \href{https://www.thejot.net/article-preview/?show_article_preview=1279}{Lodestar profile}, \emph{Journal of Ocean Technology}, \textbf{16}:{3}.
}

\cvitem{Nov, 2021}{
	``Predicting depth of entrained air and seafloor boundaries: DeepSense's Echofilter Model'', \href{https://www.thejot.net/article-preview/?show_article_preview=1285}{Trade Winds profile}, \emph{Journal of Ocean Technology}, \textbf{16}:{3}.
}

\cvitem{Mar, 2021}{
	``AI software developed in N.S. provides glimpse into wild and murky Bay of Fundy'', \href{https://www.cbc.ca/news/canada/nova-scotia/scientists-differentiate-fish-air-bubbles-1.5964650}{News article}, \emph{CBC}.
}


%----------------------------------------------------------------------------------------
\clearpage

\section{Supervision experience}

\cventry{since 2024}{ZeMing Gong}{Master of Computer Science}{Simon Fraser University}{Topic: Multimodal alignment for insect biodiversity modelling.}{Co-supervised by Prof.~\AngelChang{}}
\cventry{since 2023}{John Quinto}{Master of Computer Science}{University of Guelph}{Topic: Creating instance segmentation masks for bulk images of insects.}{Co-supervised by Prof.~\GrahamTaylor{}}
\cventry{since 2023}{Finlay Miller}{Master of Computer Science}{Dalhousie University}{Topic: Interactive MIDI generation.}{Co-supervised by Prof.~\SageevOore{}}
\cventry{2023 -- 2024}{Pablo Millán Arias}{Ph.D. in Computer Science}{University of Waterloo}{\href{https://uwspace.uwaterloo.ca/bitstream/handle/10012/20581/MillanArias_Pablo.pdf?sequence=5}{Thesis}: ``Deep Unsupervised Learning for Biodiversity Analyses''.}{Co-supervised by Prof.~\LilaKari{}}
\cventry{2021 -- 2022}{Amit Baroi}{Master of Resource \& Environmental Management}{Dalhousie University}{and DeepSense Data Science Intern, Topic: Building a global benthic habitat imagery dataset.}{Co-supervised by Prof.~\ThomasTrappenberg{}}
\cventry{2020 -- 2022}{Isaac Xu}{Master of Computer Science}{Dalhousie University}{Topic: Addressing the impact of imbalanced data in self-supervised learning.}{Co-supervised by Prof.~\ThomasTrappenberg{}}
\cventry{2020 -- 2022}{Shakhboz Abdulazizov}{Master of Computer Science}{Dalhousie University}{Topic: Learning multi-modal representations of benthic habitat data.}{Co-supervised by Prof.~\ThomasTrappenberg{}}
\cventry{2019 -- 2020}{Robert Earle}{Honours Computer Science \& Statistics}{Dalhousie University}{Thesis: ``Behaviour Of Higher Order Activation Functions''.}{Co-supervised by Prof.~\SageevOore{}}
\cventry{2018 -- 2019}{Nicholas Barreyre}{Combined Honours Bachelor of Science}{Dalhousie University}{Thesis: ``Conditional Sequence Generation: Controlling Neural Language Models For Music And Text''.}{Co-supervised by Prof.~\SageevOore{}}
\cventry{2018 -- 2019}{Nicholas Meade}{Honours Bachelor of Computer Science}{Dalhousie University}{Thesis: ``Conditional Sequence Generation: Controlling Neural Language Models For Music And Text''.}{Co-supervised by Prof.~\SageevOore{}}


%----------------------------------------------------------------------------------------
%\clearpage

% \section{Teaching experience}
%
% \cventry{Autumn, 2013}{Neural Computation}{Tutor}{University of Edinburgh}{}{}

%----------------------------------------------------------------------------------------
%\clearpage

\section{Online Presence}

\cvitem{G Scholar}{\href{https://scholar.google.com/citations?user=ZFPhxuAAAAAJ}{Scott C. Lowe}}{}{}{}{}{}
\cvitem{Blog}{\textnormal{\href{https://scottclowe.com}{scottclowe.com}}}{}{}{}{}{}
\cvitem{GitHub}{\textnormal{\href{https://github.com/scottclowe}{github.com/scottclowe}}}{}{}{}{}{}
\cvitem{LinkedIn}{\textnormal{\href{http://linkedin.com/in/scottclowe}{linkedin.com/in/scottclowe}}}{}{}{}{}{}
\cvitem{StackOverflow}{\textnormal{\href{https://stackoverflow.com/users/1960959/scottclowe}{stackoverflow.com/users/1960959/scottclowe}}}{}{}{}{}{}
\cvitem{Kaggle}{\textnormal{\href{https://www.kaggle.com/scottclowe}{kaggle.com/scottclowe}}, Kaggle Competitions Master}{}{}{}{}{}


%----------------------------------------------------------------------------------------
% \clearpage
% \section{Responsibilities}
%
% \cvitem{2010--2011}{Durham University Humanist and Secularist Society, Webmaster}
% \cvitem{2009--2011}{Collingwood College JCR, Webmaster}
% \cvitem{2009--2011}{University of Durham Orienteering Club, Webmaster}

%----------------------------------------------------------------------------------------
% REFERENCES
%----------------------------------------------------------------------------------------
% \clearpage

% \section{References}
%
% \cvitem{}{References available upon request.}

% \cvlistitem{Prof. Thomas Trappenberg,\\
% Faculty of Computer Science,\\
% Dalhousie University,\\
% 6050 University Avenue\\
% PO BOX 15000\\
% Halifax, NS B3H 4R2\\
% Canada\\
% \href{mailto:tt@cs.dal.ca}{tt@cs.dal.ca}\\
% }
% \cvlistitem{Dr. Sageev Oore,\\
% Faculty of Computer Science\\
% Dalhousie University\\
% 6050 University Avenue\\
% PO BOX 15000\\
% Halifax, NS B3H 4R2\\
% Canada\\
% \href{mailto:sageev@dal.ca}{sageev@dal.ca}\\
% }
% \cvlistitem{Prof. Mark van Rossum,\\
% Chair and Director/Neuralcomputation Research Group,\\
% School of Psychology,\\
% University of Nottingham,\\
% University Park\\
% Nottingham, NG7 2RD, UK\\
% \href{mailto:Mark.vanRossum@nottingham.ac.uk}{Mark.vanRossum@nottingham.ac.uk}\\
% % % Reader in Computational Neuroscience,\\
% % % Director of Doctoral Training Centre in Neuroinformatics,\\
% % School of Informatics,\\
% % University of Edinburgh,\\
% % Edinburgh, EH8 9AB, UK\\
% % \href{mailto:mvanross@inf.ed.ac.uk}{mvanross@inf.ed.ac.uk}\\
% }
% \cvlistitem{Prof. Stefano Panzeri,\\
% % Senior Researcher in Neural Computation,\\
% Director of the Neural Computation Laboratory,\\
% Center for Neuroscience and Cognitive Systems,\\
% Istituto Italiano di Technologia,\\
% Bettini 31, Rovereto (Tn), Italy\\
% \href{mailto:stefano.panzeri@iit.it}{stefano.panzeri@iit.it}\\
% }
% \cvlistitem{Dr. Nathalie Rochefort,\\
% Wellcome Trust and Royal Society Sir Henry Dale fellow,\\
% Centre for Integrative Physiology,\\
% University of Edinburgh,\\
% Edinburgh, EH8 9XD, UK\\
% \href{mailto:n.rochefort@ed.ac.uk}{n.rochefort@ed.ac.uk}\\
% }
% % \cvlistitem{Additional references available on request.}

%----------------------------------------------------------------------------------------
%
\end{document}
